---
title: "Complete normal results on platelets in GAIT 2 Study"
author: "Miquel Vàzquez-Santiago"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    toc: true
    keep_md: true
---

```{r options, echo = F}
opts_chunk$set(fig.path = "figures/",
							 comment = NA,
							 tidy = F,
							 message = F,
							 warning = F,
							 echo = F,
							 results = 'verbatim')



```{r par}
alpha <- 0.05
```

# Library

```{r inc, cache = F}
library(knitr)
library(rmarkdown)
library(devtools)

load_all("~/R/x86_64-pc-linux-gnu-library/3.3/solaris-master/")
library(lmerTest)

library(gridExtra)
library(lattice)
library(RColorBrewer)

library(broom)
library(pander)
```

```{r settings, cahe = F}
theme_set(theme_light())

panderOptions('table.split.table', Inf)
panderOptions('knitr.auto.asis', FALSE)

# par `models`
lmerControl <- lmerControl(check.nobs.vs.nlev = "ignore",
							 check.nobs.vs.nRE = "ignore", check.nobs.vs.rankZ = "ignore")
```

# Load data

```{r data, cache = F, echo = T}
# relation
load("~/Datasets/GAIT_2/K.RData")

# general data
load_all()
dat <- thesis.norm.platelets()

## check
stopifnot(sum(is.na(dat$IPFCT)) == 86)
stopifnot(sum(is.na(dat$PFAepin)) == 34)
```

# Models

```{r models}
# variables
vars <- thesis.traits.platelets()
models <- list()

# function
for(i in vars){
	cat("###", i, "\n")

	covlist <- thesis.covlist_plt.norm(i)
	mods <- thesis.mod.norm(dat, i, covlist)

models[[length(models) + 1]] = mods
}




